Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

Supervised link prediction methods convert the problem into a binary classification task where links present in the network (at a given time) are considered as positive instances and a subset of all the non links are considered as negative instances. Following \cite{matrix-factorization}, we can further group these methods into four classes: feature-based models, graph regularization models, latent class models and latent feature models. 
A Bayesian nonparametric approach is used in \cite{nonparametric} to compute a nonparametric latent feature model that does not need a user defined number of latent features but rather induces it as part of the training phase. 
In \cite{matrix-factorization} a matrix factorization approach is used to extract latent features that can take into consideration the output of an unsupervised method. The authors show impressive increase in predictive performance when considering a ranking loss function to deal with the imbalance problem (i.e. a much larger number of negative vs positive instances).

>>>>

Supervised link prediction methods convert the problem into a binary classification task where links present in the network (at a given time) are considered as positive instances and a subset of all the non links are considered as negative instances. Following \cite{matrix-factorization}, we can further group these methods into four classes: feature-based models, graph regularization models, latent class models and latent feature models. 
A Bayesian nonparametric approach is used in \cite{nonparametric} to compute a nonparametric latent feature model that does not need a user defined number of latent features but rather induces it as part of the training phase. 
In \cite{matrix-factorization} a matrix factorization approach is used to extract latent features that can take into consideration the output of an arbitrary unsupervised method. The authors show a significant increase in predictive performance when considering a ranking loss function suitable for  the imbalance problem, i.e. when the number of negative is much larger than the number of positive instances.
